Disclosure of Product System Models in Life Cycle Assessment: Achieving Transparency and Privacy

### 2017-10-30 aggregation/agg-semantic.tex
morning tweaks
paltry work today
minor discussion work

For each row in $A_d$ containing a non-zero entry, the author must unambiguously identify the version of the database used, as well as the exact process and reference flow used from the background database; the dimension (reference quantity or unit) of each reference flow must be specified; and the sign of the numeric entry in $A_d$ must be consistent with the implementation of the process in the background database.

Similarly, for each row in $B_f$ containing a non-zero entry, the author must unambiguously identify the substance being exchanged with the environment, the compartment or context into which it is being exchanged, and the reference quantity or unit associated with the flow.  Sign consistency must also be assured.  If LCIA indicator results are included, the author must also unambiguously identify the method computed (identity of $\mathbf{e}$).

For the reader's part, the reader must be able to produce an $\mathbf{e}$ vector that matches the one used by the author and identify which entries correspond with which

@@

>>>>

\subsection{Avoiding Ambiguous Disclosures}

@@

Multiple background databases

\subsection{Stable Semantic References}
